It has been highlighted that the complete solution of a hyperbolic system in elastic-plastic solids requires to know \textit{a priori} the wave structure.
The object of this section is to study the mathematical properties of the loading functions \eqref{eq:loading_func} in order to get some clues about the stress paths.
It is believed that the information thus earned could be used to accurately approximate the integration of equations \eqref{eq:integral_example}.
First, general properties holding regardless of the loading conditions are highlighted.
Next, the equations are specialized to plane stress and plane strain cases.

\subsection{The general case}
To begin with, let us look at the product of the two loading functions in a direction of space.
Given the left eigenvectors of the acoustic tensor in equation \eqref{eq:eigenvectAcc}, one has for instance:
%Indeed, considering the left eigenvectors of the acoustic tensor given in equation \eqref{eq:eigenvectAcc}, the product $\psi^s_1\psi^f_1$ reads:
\begin{equation*}
  \psi^s_1\psi^f_1 = \frac{l^1_2}{l^1_1}\: \frac{l_2^2}{l^2_1}  
\end{equation*}
Since the eigenvectors of symmetric second-order tensors all satisfy $\vect{l}^1 \cdot \vect{l}^2=0$, it comes out that the above product is equal to $-1$.
Hence, the loading paths resulting from the integration of the ODEs involving $\psi^s_1$ and $\psi^f_1$ are perpendicular in the stress space.
The same goes for $\psi^s_2 $ and $\psi^f_2 $.
Although this orthogonality has already been noticed for particular plane strain and plane stress cases \cite{Clifton,Ting68}, \emph{the generic formulation proposed here shows that this is valid for all problems in two space dimensions}. 
As a result, the study can be restricted to one function in each direction, say $\psi_1^s$ and $\psi_2^s$.


Second, if the function $\psi_1^s$ vanishes at some point of the stress space, the projection in the $(\sigma_{11},\sigma_{12})$ plane of the loading path followed within a slow wave is vertical according to the ODE \eqref{eq:sigSlow_n=e1} (\textit{i.e} $d\sigma_{11}=0$).
Conversely, if $\psi_1^s\rightarrow \infty$, the loading path is horizontal in the $(\sigma_{11},\sigma_{12})$ plane (\textit{i.e} $d\sigma_{12}=0$).
%Looking for vanishing $\psi^f_1$ or $1/\psi^f_1$ amounts to finding roots of the components of $\vect{l}^2$:
These situations respectively correspond to:
\begin{align}
  \label{eq:first_root}
  \psi_1^s = 0  & \Leftrightarrow A_{12} =0  \\
  \label{eq:second_root}
  \psi_1^s \rightarrow \infty & \Leftrightarrow A_{22} -\omega_1 =0
\end{align}
In particular, if $A_{12}=0$ the denominator of $\psi_1^s$ reads:
\begin{equation}
  A_{22} -\omega_1 = \frac{1}{2}\(A_{22} -A_{11} -\sqrt{(A_{11} -A_{22} )^2 + 4A_{12}^2 }\) = \frac{1}{2}\(A_{22} -A_{11} -\abs{A_{11} -A_{22}}\vphantom{\sqrt{(A_{11} -A_{22} )^2 + 4A_{12}^2 }}\) = -\left\langle A _{11}-A _{22}  \right\rangle
\end{equation}
where $\left\langle \bullet \right\rangle=\frac{1}{2}\(\bullet + \abs{\bullet}\)$ denotes the positive part operator.
Therefore, if $A_{12} =0$ and $A_{11} \neq A_{22} $, one has $\psi^s_1 =0$ and hence $\psi^f_1 \rightarrow -\infty $ by orthogonality.
If moreover $A_{11}  = A_{22} $, both components of the eigenvectors vanish and the functions $\psi^s_1$ and $\psi^f_1$ are undetermined.
Note also that in this case, the characteristic speeds of simple waves are identical according to  equations \eqref{eq:eigenAcc1} and \eqref{eq:eigenAcc2}.
  % \begin{equation}
  %   \label{eq:diff_celerities}
  %   \rho c_f^2 - \rho c_s^2 = \sqrt{(A_{11}-A_{22})^2+{4A_{12}}^2} 
  % \end{equation}
  % Then, it follows that the simultaneous satisfaction of conditions \eqref{eq:first_root} and \eqref{eq:second_root} leads to
As a result, the situation $c_f=c_s$ corresponds to a loss of hyperbolicity of the system.

Analogously, the function $\psi_2^s$ is such that:
\begin{align}
    \label{eq:first_root_psi2cp}
    \psi_2^s \rightarrow \infty  & \Leftrightarrow A_{12} =0  \\
    \label{eq:second_root_psi2cp}
    \psi_2^s =0 &  \Leftrightarrow A_{22} -\omega_1 =0
\end{align}
Therefore, if both conditions $A_{12}=0$ and $A_{11} =A_{22}$ are satisfied, the system is no longer hyperbolic with characteristic speeds of fast and slow waves that are identical.

According to the ODEs of table \ref{tab:simpleWavesEquations}, the particular values of the loading functions $\psi_i^{s,f}$ through the simple waves propagating in direction $\vect{e}_i$ for $i=\{1,2\}$, provide information about the loading paths in the stress space.
First, $\psi^{s,f}_i =0$ leads to $d\sigma_{ii}=0$ (no sum on $i$) so that the longitudinal stress is constant within the simple wave.
Conversely, with the loading functions tending to infinity, the stress $\sigma_{12}$ does not vary.
Notice that the coefficients $\alpha_{ij}$ of the left eigenvector of the Jacobian matrix associated with the zero eigenvalue \eqref{eq:null_left_eigen} also have to be regarded.
Nevertheless, those terms resulting from products of the components of the elastoplastic tangent modulus have complex expressions and are assumed to have non-zero values in the remainder of the paper.

The above discussions are now specified to the plane strain and plane stress cases, for which loading conditions leading to $A_{12} =0$ and $A _{11}-A _{22}=0$ are identified.



\subsection{The plane strain case}
The case of plane strain is first considered by using the elastoplastic tangent modulus so that the components of the acoustic tensor for $\vect{n}=\vect{e}_1$ read:
% The elastoplastic tangent modulus under consideration is now that given in equation \eqref{eq:elastoplastic_tangent}, so that the components of the acoustic tensor for $\vect{n}=\vect{e}_1$ read: 
\begin{align}
  \label{eq:DP_A11}
  & A_{11}^{ep}= C_{1111}^{ep} = \lambda + 2\mu -\beta s_{11}^2 \\
  \label{eq:DP_A22}
  & A_{22}^{ep}= C_{2121}^{ep}= \mu -\beta s_{12}^2 \\
  \label{eq:DP_A12}
  & A_{12}^{ep}= C_{1121}^{ep}=-\beta s_{11}s_{12}
\end{align}
The associated eigenvalues are then:
\begin{align}
  \label{eq:eigen_acc_DP1}
  & \rho c_s^2 =  - \frac{\sqrt{\[\lambda + \mu -\beta (s_{11}^2-s_{12}^2) \]^2 +4(\beta s_{11}s_{12})^2}}{2}  
   + \frac{\lambda +3\mu -\beta (s_{11}^2+ s_{12}^2)}{2}
   \\
  \label{eq:eigen_acc_DP2}
  & 
    \rho c_f^2 =    \frac{\sqrt{\[\lambda + \mu -\beta (s_{11}^2-s_{12}^2) \]^2 +4(\beta s_{11}s_{12})^2}}{2}  
     + \frac{\lambda +3\mu -\beta (s_{11}^2+ s_{12}^2)}{2}
\end{align}
Subtracting equations \eqref{eq:DP_A11} and \eqref{eq:DP_A22}, one gets: $A_{11}^{ep}-A_{22}^{ep}= \lambda + \mu -\beta \(s_{11}^2-s_{12}^2\)$.
Hence, the equation $A_{11}^{ep}-A_{22}^{ep}=0$ admits a set of solutions in the deviatoric stress space.
On the other hand, we see from equation \eqref{eq:DP_A12} that $A_{12}^{ep}$ vanishes for $s_{12}=0$ or $s_{11}=0$.
% Recall that $A^{ep}_{12}=0$ leads to vertical and horizontal loading paths across slow and fast waves respectively. 
Each solution is studied in more details below.

%% Sign of one of the functions psi... but not used afterwards
% We first study the sign of the functions $\psi^f$ by noticing that $\mu=\rho c_2^2$ so that $A_{22}^{ep}$ may be rewritten to yield:
% \begin{equation*}
%   \psi^f = -\frac{A_{12}^{ep}}{A_{22}-\rho c_f^2}= -\frac{\beta s_{11}s_{12}}{\rho c_f^2-\rho c_2^2 +\beta s_{12}^2 }
% \end{equation*}
% Since the denominator is positive for $c_f \geq c_2$, it comes out that $\sign (\psi^f) = - \sign(s_{12}) \sign(s_{11})$. Moreover, two roots of the loading function $\psi^f$ can be identified.

%\textbf{Condition $s_{12}=0$}: 
\subsubsection{Condition $s_{12}=0$}
% \review{According to \textsc{Raniecki} \cite[ch.3 p.173]{mandel_book}, this case leads to $c_s =c_2$.}

According to equations \eqref{eq:eigen_acc_DP1} and \eqref{eq:eigen_acc_DP2}, the eigenvalues of the acoustic tensor become:
\begin{align*}
  & \rho c_s^2 = \frac{1}{2}\( \lambda +3\mu -\beta s_{11}^2 - \abs{\lambda + \mu -\beta s_{11}^2 } \) \\
  & \rho c_f^2 = \frac{1}{2}\( \lambda +3\mu -\beta s_{11}^2 + \abs{\lambda + \mu -\beta s_{11}^2 } \)
\end{align*}
Two cases are to be considered:
\begin{itemize}
\item[(i)] if $\beta s_{11}^2 < \lambda + \mu$, the expression further reduces to:
  \begin{align*}
    & \rho c_s^2 = \mu \\
    & \rho c_f^2 = \lambda +2\mu -\beta s_{11}^2 
  \end{align*}
  The characteristic speed of slow waves is therefore equivalent to that of elastic shear waves for plane strain $c_s=c_2=\sqrt{\mu/\rho}$. 
\item[(ii)] if $ \lambda + \mu - \beta s_{11}^2 <0$, the characteristic speeds read: 
  \begin{align*}
    & \rho c_s^2 = \lambda +2\mu -\beta s_{11}^2  \\
    & \rho c_f^2 =  \mu 
  \end{align*}
  Therefore, the celerity of fast waves reduces to that of elastic shear waves.
  Note, however, that the characteristic speed of slow waves remains real if and only if $\lambda +2\mu >\beta s_{11}^2$.
  One then gets the following bounds: $\lambda +2\mu > \beta s_{11}^2 > \lambda +\mu$.
\end{itemize}
Note that the two above situations lead to the propagation of one neutral wave in the medium.
  
At last, the equality $\beta s_{11}^2 = \lambda + \mu$ leads to $A_{11}^{ep}-A_{22}^{ep}=0$ and hence, to undetermined loading functions. 
%% Set of admissible values for s11 (depends on s itself)
% It then appears that the values of $s_{11}$ ensuring hyperbolicity of the system are:
% \begin{equation}
%   s_{11} \in ]-\infty,-\sqrt{\frac{\lambda + \mu}{\beta}}[\: \cup\: ]-\sqrt{\frac{\lambda + \mu}{\beta}},\sqrt{\frac{\lambda + \mu}{\beta}}[\: \cup \:]\sqrt{\frac{\lambda + \mu}{\beta}} ,\infty[
% \end{equation}

%% Discussion about the loading path direction
% Recall that $\psi^f_1$ tending to infinity implies that the loading path are horizontal in $(\sigma_{11},\sigma_{12})$ plane and hence, the fast wave has no influence on the shear stress if, and only if, $\sigma_{12}=0$ downstream.
% Conversely, the stress paths through slow simple waves are vertical.
% Moreover, with regard the last row of table \ref{tab:simpleWavesEquations}, $\sigma_{22}$ is also unchanged in that case.
% As a consequence, if the initial state is shear-free the solution no longer contain combined waves, but longitudinal stress and shear stress simple waves.

% \textbf{Condition $s_{11}=0$}:
\subsubsection{Condition $s_{11}=0$}
Considering the relation \eqref{eq:plane_strain_stress33} between the stress components for plane strain, one writes:
\begin{equation*}
  s_{11}= \frac{2}{3}\sigma_{11}-\frac{1}{3}(\sigma_{22}+\nu(\sigma_{11}+\sigma_{22})-E\eps^p_{33})
\end{equation*}
so that $s_{11}=0$ is equivalent to:
\begin{equation}
  \label{eq:plane_strain_s11=0}
  \sigma_{11}=\frac{1+\nu}{2-\nu}\sigma_{22}-E\eps^p_{33}
\end{equation}
In contrast to what has been seen previously, the functions $\psi^{s,f}$ cannot be undetermined in the case $s_{11}=0$ since the equation $A_{11}^{ep}-A_{22}^{ep}=\lambda + \mu + \beta s_{12}^2=0$ does not admit real solutions.
Nevertheless, the stress state \eqref{eq:plane_strain_s11=0} yields the following characteristic speeds:
\begin{align*}
  & \rho c_s^2 = \mu -\beta s_{12}^2 \\
  & \rho c_f^2 = \lambda +2\mu 
\end{align*}
so that the celerity of fast waves identifies with that of elastic pressure waves under plane strain $c_f=c_1=\sqrt{(\lambda + 2\mu)/\rho}$. %$
Once again, this case corresponds to the propagation of a neutral wave.


%%%% n=e2
$\newline$
The same analysis can be carried out in the direction $\vect{n}=\vect{e}_2$ by considering the following acoustic tensor components:
\begin{align}
  \label{eq:DP_A11_n2}
  & A_{11}^{ep}= C_{1212}^{ep} = \mu -\beta s_{12}^2 \\
  \label{eq:DP_A22_n2}
  & A_{22}^{ep}= C_{2222}^{ep}= \lambda + 2\mu -\beta s_{22}^2 \\
  \label{eq:DP_A12_n2}
  & A_{12}^{ep}= C_{1222}^{ep}=-\beta s_{22}s_{12}
\end{align}
The characteristic speeds are then:
\begin{align}
  \label{eq:eigen_acc_DP1_n2}
  & \rho c_s^2 = - \frac{\sqrt{\[\lambda +\mu -\beta (s_{22}^2-s_{12}^2) \]^2 +4(\beta s_{22}s_{12})^2}}{2} 
    + \frac{\lambda +3\mu -\beta (s_{22}^2+ s_{12}^2)}{2}   
   \\
  \label{eq:eigen_acc_DP2_n2}
  &
      \rho c_f^2 =   \frac{\sqrt{\[\lambda +\mu -\beta (s_{22}^2-s_{12}^2) \]^2 +4(\beta s_{22}s_{12})^2}}{2}
      + \frac{\lambda +3\mu -\beta (s_{22}^2+ s_{12}^2)}{2}   
\end{align}
With these expressions, the same remarks as for $\vect{n}=\vect{e}_1$ can obviously be made by replacing $s_{11}$ with $s_{22}$.

Among the above results, the most significant arises from the condition $s_{12}=0$.
Indeed, it has been seen that $A_{12}^{ep}=0$ leads to $\psi_1^s=0$ and $\psi^s_2\rightarrow \infty$ in such a way that the corresponding loading paths in the $(\sigma_{11},\sigma_{12})$ plane are respectively vertical and horizontal.
Under the orthogonality property of the loading functions, the stress path followed in a fast wave propagating in the direction $\vect{e}_1$ is horizontal in the same plane.
Hence, if the path through a fast wave intersects the plane $\sigma_{12}=0$, the shear stress component remains constant afterwards.
The same result holds for the slow wave propagating in the direction $\vect{e}_2$.
The above conclusion are summarized in table \ref{tab:stress_paths_properties}.
\begin{table*}[h!]
  \centering
  \input{tabular/stress_paths}
  \caption{Loading paths projected on the ($\sigma_{11},\sigma_{12}$) plane followed across slow and fast simple waves, under the condition $\sigma_{12}=0$ assuming that $A_{11}^{ep}-A_{22}^{ep}\neq 0$.}
  \label{tab:stress_paths_properties}
\end{table*}
\subsection{The plane stress case}
% The elastoplastic tangent modulus under consideration is now that given in equation \eqref{eq:CP_constitutive}.
As mentioned in section \ref{sec:2dproblem}, a suitable elastoplastic tangent modulus $\widetilde{\Cbb}^{ep}$ is now under consideration.
Let's first focus on $\psi_1^s$ related to the vector $\vect{n}=\vect{e}_1$.
Thus:
\begin{align}
  \label{eq:CP_A11}
  &
      \widetilde{A}_{11}^{ep}= \: C^{ep}_{1111} - \frac{(C^{ep}_{1133})^2}{C^{ep}_{3333}} =\:\lambda + 2\mu -\beta s_{11}^2 -\frac{\(\lambda -\beta s_{11}s_{33}\)^2}{\lambda + 2\mu - \beta s_{33}^2}  \\
  \label{eq:CP_A22}
  &
      \widetilde{A}_{22}^{ep}=  \: C^{ep}_{2121} - \frac{(C^{ep}_{2133})^2}{C^{ep}_{3333}} =\:\mu - \beta s_{12}^2 -\frac{\(\beta s_{12}s_{33}\)^2}{\lambda + 2\mu - \beta s_{33}^2}   
\\
  \label{eq:CP_A12}
  &
      \widetilde{A}_{12}^{ep} = \: C^{ep}_{1121} - \frac{C^{ep}_{1133}C^{ep}_{1233}}{C^{ep}_{3333}} =\:\beta s_{12} \frac{\lambda s_{33} - (\lambda + 2\mu)s_{11} }{\lambda + 2\mu - \beta s_{33}^2}
\end{align}
In order to ensure the hyperbolicity of the system, the components of the acoustic tensor also have to be defined, that is $C^{ep}_{3333}> 0$, which leads to:
\begin{equation*}
  \lambda + 2\mu - \beta s_{33}^2 > 0 \quad \Leftrightarrow \quad s_{33}^2 < \frac{\lambda + 2\mu}{\beta}
\end{equation*}
Second, from equation \eqref{eq:CP_A12}, $\widetilde{A}_{12}^{ep}$ admits two roots in terms of the components of the deviatoric stress tensor, namely: 
\begin{equation}
  s_{12}=0 \quad ; \quad s_{11}= \frac{\lambda}{\lambda+2\mu}s_{33}
\end{equation}
In terms of the components of the Cauchy stress tensor, these conditions read:
\begin{equation}
  \label{eq:CP_roots}
  \sigma_{12}=0 \quad ; \quad \sigma_{11}=\frac{2\mu}{3\lambda+4\mu}\sigma_{22}
\end{equation}
% Hence, the loading path through a slow simple wave is vertical, that is $\psi^s_1 = 0$, for stress values satisfying \eqref{eq:CP_roots}, providing that the $\widetilde{A}_{11}^{ep}$ and $\widetilde{A}_{22}^{ep}$ are not equal.
% Conversely, such stress states yield horizontal path through a fast wave.


% \textbf{Case $s_{12}=0$ :}
% \begin{align}
%   & \rho c_s^2 =\frac{1}{2}\(\widetilde{A}_{11}^{ep}+\widetilde{A}_{22}^{ep} - \abs{\widetilde{A}_{11}^{ep}-\widetilde{A}_{22}^{ep}}\) \\
%   & \rho c_f^2 =\frac{1}{2}\(\widetilde{A}_{11}^{ep}+\widetilde{A}_{22}^{ep} + \abs{\widetilde{A}_{11}^{ep}-\widetilde{A}_{22}^{ep}}\)
% \end{align}

If on the other hand the vector $\vect{n}=\vect{e}_2$ is considered, the acoustic tensor components read:
\begin{align}
    \label{eq:CP_A11_n=e2}
    & \widetilde{A}_{11}^{ep}= C^{ep}_{1212} - \frac{(C^{ep}_{1233})^2}{C^{ep}_{3333}} = \mu -\beta s_{12}^2 -\frac{\(\lambda -\beta s_{12}s_{33}\)^2}{\lambda + 2\mu - \beta s_{33}^2} \\
    \label{eq:CP_A22_n=e2}
    & \widetilde{A}_{22}^{ep}= C^{ep}_{2222} - \frac{(C^{ep}_{2233})^2}{C^{ep}_{3333}}= \lambda +2\mu - \beta s_{22}^2 -\frac{\(\beta s_{22}s_{33}\)^2}{\lambda + 2\mu - \beta s_{33}^2} \\
    \label{eq:CP_A12_n=e2}
    & \widetilde{A}_{12}^{ep} = C^{ep}_{1222} - \frac{C^{ep}_{1233}C^{ep}_{2233}}{C^{ep}_{3333}} =\beta s_{12} \frac{\lambda s_{33} - (\lambda + 2\mu)s_{22} }{\lambda + 2\mu - \beta s_{33}^2}
    %     \label{eq:CP_A11_n=e2}
    % & \widetilde{A}_{11}^{ep}=  \mu -\beta s_{12}^2 -\frac{\(\lambda -\beta s_{12}s_{33}\)^2}{\lambda + 2\mu - \beta s_{33}^2} \\
    % \label{eq:CP_A22_n=e2}
    % & \widetilde{A}_{22}^{ep}= \lambda +2\mu - \beta s_{22}^2 -\frac{\(\beta s_{22}s_{33}\)^2}{\lambda + 2\mu - \beta s_{33}^2} \\
    % \label{eq:CP_A12_n=e2}
    % & \widetilde{A}_{12}^{ep} = \beta s_{12} \frac{\lambda s_{33} - (\lambda + 2\mu)s_{22} }{\lambda + 2\mu - \beta s_{33}^2}
\end{align}
These expressions are similar to those obtained before with $s_{22}$ instead of $s_{11}$.
It comes out that $\widetilde{A}_{12}^{ep}$ admits two roots in the case $\vect{n}=\vect{e}_2$:
\begin{equation}
  \label{eq:CP_roots_n=e2}
  \sigma_{12}=0 \quad ; \quad \sigma_{22}=\frac{2\mu}{3\lambda+4\mu}\sigma_{11}
\end{equation}

The complexity introduced by the plane stress tangent modulus prevents finding other singular configurations for the hyperbolic system. 
In particular, it is difficult to deal with the equation $\widetilde{A}^{ep}_{11}=\widetilde{A}^{ep}_{22}$ due to the expressions given in equations \eqref{eq:CP_A11} and \eqref{eq:CP_A22}.
Nevertheless, since the stress state $s_{12}=0$ also constitutes a singular point for plane stress, the same remarks as those made for the plane strain loading path hold.
Namely, $\sigma_{12}$ becomes constant if it falls to zero along the loading path followed inside a fast (\textit{resp. slow}) wave propagating in direction $\vect{e}_1$ (\textit{resp. $\vect{e}_2$}), as summarized in table \ref{tab:stress_paths_properties}.
%Namely, if $\sigma_{12}$ falls to zero along the loading path followed inside a fast (\textit{resp. slow}) wave propagating in direction $\vect{e}_1$ (\textit{resp. $\vect{e}_2$}), is restricted to that value.
%As we shall see below, more singular behaviors can be identified for plane strain.



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "manuscript"
%%% End:
