\documentclass[10pt,a4paper,twoside]{report}

\input{preamble}

\begin{document}
\newpage

\section*{Acknowledgments}
These last years spent in Nantes as a bachelor, master, and PhD student have been a real pleasure and will leave me full of good memories.

First, I would like to thank the directors of this thesis, Laurent Stainier and Thomas Heuz{\'e}, for trusting me for these research.
They both guided me very patiently throughout this work, especially during the reviewing of manuscripts.
In addition, I must emphasize the very good musical tastes of Laurent Stainier and the gastronomic tastes of Thomas Heuz{\'e}, which have been the subject of interesting discussions.
Owing to their moral values and scientific skills, I have been very happy to work with them.

Second, I am grateful to several faculty members met when I was a master student at Nantes University, who then became colleagues: Jean-Christophe Thomas, Mathilde Chevreuil, Marc Fran{\c c}ois, Anh Le van, Rabah Bouzidi and Laurent Gornet. 
Their courses showed me how much computational mechanics can be interesting though challenging.

Third, I also want to thank my "building F colleagues": Baptiste and Erwan (along with the other CBEM organizers), Pierre, Rohit, Jorge, Beno{\^i}t, Romain, Simon, George, Tauno, Abdullah, Zolt{\'a}n, C{\'e}cile, Daria, Quentin, Steven, Fabien, Hong-Duc, Elie, Rhapha{\"e}l, Adrien and Ataollah, as well as the "building T people": Julie, Marie and Nicolas.
They all contributed to an atmosphere which helps during difficult times. 
This reminded me the good old days at the university with Jan, Cocaud, Laporte, Le Mouel, Mac{\'e}, "Le Commodore" Varin and Claude.

Fourth, I am thankful to Cynthia and Marine who managed the administrative difficulties that I encountered.
Moreover, I thank Anthony who saved me by lending me his laptop the day of my defense.

Fifth, I would like to thank Morgane for considerably supporting me and for undergoing my mood swings.
I also must thank Doroth{\'e}e, Hana{\"e} and Ga{\"e}l for lending me their house so that I could write peacefully.


At last, I am grateful to my friends and family for coming to my defense and to the celebration of my birthday the next day. 
They all supported me during these three years, especially my sister Emmanuelle by the end of her pregnancy.


\tableofcontents{}


%% Chapter 1: Introduction
\chapter{Introduction}
\input{chapter1/mainChapter1}
% Parler du choix des méthodes explicite pour suivre les charactéristics Vs implicites


%% Chapter 2: Hyperbolic partial differential equations
\chapter{Hyperbolic partial differential equations for solid dynamics}
\label{chap:chap2}
\input{chapter2/mainChapter2}

%% Chapter 3: The Discontinuous Galerkin Material Point Method
\chapter{The Discontinuous Galerkin Material Point Method}
\label{chap:chap3}
\input{chapter3/mainChapter3}

%% Chapter 4: Numerical Results
\chapter{Numerical Results}
\label{chap:chap4}
\input{chapter4/mainChapter4}

%% Chapter 5: Contribution to the solution of two-dimensional elastoplastic problems
\chapter{Contribution to the solution of elastic-plastic hyperbolic problems in two space dimensions}
\label{chap:chap5}
\input{chapter5/mainChapter5}


%% Chapter 6: Conclusion
\chapter{Conclusion and future works}
\input{chapter6/mainChapter6}


\addcontentsline{toc}{chapter}{References}
\bibliographystyle{ieeetr}
\bibliography{Biblio}

% \newpage



% \AddToShipoutPicture*{\BackgroundBPage}
% \thispagestyle{empty}
% ~~\\
% \ClearShipoutPicture

\end{document}

%%% Local Variables:
%%% mode: latex
%%% ispell-local-dictionary: "american"
%%% TeX-master: t
%%% End:
