\chapter{The Discontinuous Galerkin Material Point Method}

\section*{Introduction}
It has been highlighted in the previous chapter that even though exact solutions of hyperbolic systems have been derived, it is not possible in general. It is indeed well known that in addition to the mathematical complexity of PDEs, physics often involves multidimensional problems in solid domains with complex geometries that cannot be solved analytically. Numerical strategies may then be employed in order to compute an approximate solution to such problems.

Since the early 50's, plenty of numerical methods that consist mainly in mesh-based schemes, that is methods subdividing a complex domain into elements of simple shapes in which an approximate solution is sought, have been developed (\textit{finite element \cite{Belytschko}, finite volume \cite{Leveque} etc.}). Problems involving very large deformations may lead, however, to numerical difficulties when this kind of approaches is used with a material description (Lagrangian formulation) due to severe mesh distortions. Alternatively, Eulerian methods avoid mesh entanglement by building an approximate solution of a PDEs system on a fixed mesh that corresponds to a discretized volume of control. Nevertheless, interface tracking techniques and convection steps are required in Eulerian approaches in order to follow the boundaries and transport internal variables, which is less convenient for solid than for fluid mechanics.

The \textbf{Material Point Method} (MPM) \cite{Sulsky94} mixes the advantages of both Lagrangian and Eulerian methods in order to circumvent mesh entanglement. However, the MPM suffers from numerical diffusion and oscillations that make it unable to accurately capture the waves travelling in solids. These limitations have been the object of researches that yield significant improvements without allowing to capture discontinuities. This is the purpose of this chapter.

In what follows, a brief historical review of developments that provided to the MPM formulation is made and the original formulation is recalled in section \ref{sec:MPM}. Next, after emphasizing some shortcomings of the method, an extension of the MPM to the Discontinuous Galerkin (DG) approximation is proposed in section \ref{sec:DGMPM}. At last, the numerical analysis of the \textbf{Discontinuous Galerkin Material Point Method} (DGMPM) is performed in section \ref{sec:DGMPM_analysis} in terms of convergence and stability. Those studies of the numerical scheme show that the optimal Courant number may be reach in specific cases at the cost of first-order accuracy in velocity.



\section{The material point method}
\label{sec:MPM}
\input{chapter3/MPM}

\section{Extension of the MPM to discontinuous Galerkin approximation}
\label{sec:DGMPM}
\input{chapter3/DGMPM}

\section{Numerical analysis of the DGMPM}
\label{sec:DGMPM_analysis}
\input{chapter3/numerical_analysis}

\section*{Conclusion}
In this chapter, the formulation of the MPM has been recalled and some drawbacks of the method when applied to hyperbolic problems have been emphasized in section \ref{sec:MPM}. It has been seen that the projection of the nodal velocity field to material points inherited from FLIP, though it reduces the numerical diffusion, introduces spurious oscillations in the solution. Hence, an alternative to this mapping procedure in order to avoid numerical dissipation within the MPM without introducing numerical noise has been proposed by means of the Disontinuous Galerkin approximation in section \ref{sec:DGMPM}. The resulting DGMPM is based on the weak form of a system of conservation laws written element by element in an arbitrary computational grid in which particles can move. Interface fluxes involved in boundary integrals of the weak form result from the solution of Riemann problems at cells interfaces computed thanks to an approximate Riemann solver (see section \ref{subsec:interface_fluxes}). This method combines thus the strength of Finite Element and Finite Volume methods.

The numerical analysis of the scheme applied to the solution of one and two-dimensional linear scalar advection equations performed in section \ref{sec:DGMPM_analysis} led to the ability to determine the maximal Courant number ensuring stability for a given discretization. The method is thus characterized by a CFL number depending on the locations of particles within the computational grid, but that can be set at one in particular cases. In addition to the stability of the method, the convergence properties of the DGMPM have been compared to that of the original MPM on a one-dimensional elastic problem. While the MPM, as FEM, shows a second-order accuracy in velocity and first-order in stress, the DGMPM exhibits a first-order accuracy for both fields. The loss of accuracy has been attribué to the mapping used in the DGMPM and strategies to handle higher-order approximations have been proposed. However, the purpose of this work being the accurate capturing of waves that can be non-regular, high-order accuracy is not essential for it leads to more regularity in the numerical solution. Attention is paid to the following of waves without oscillations unlike what has been highlighted for the MPM in section \ref{sec:MPM} on the bars impact problem. The object of the next chapter is the illustration of the DGMPM performances with one and two-dimensional simulations.




%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mainManuscript"
%%% End:
